---
title: "Exercise-11"
author: "Alexandra Anderson"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
packages <- c("biscale", "car", "cleangeo", "cowplot", "geosphere", "maps",

"mapproj", "spatialreg", "spdep", "sf", "tidyverse","visreg")
library(spatialreg)

sapply(packages, require, character.only=T)
```

## Yay Torture


```{r cars, include=FALSE}
data <- read.csv('https://raw.githubusercontent.com/chrismgentry/Spatial-Regression/master/Data/childpov18_southfull.csv',

colClasses = c("character", "character", "character",

"numeric", "numeric", "numeric", "numeric",

"numeric", "numeric", "numeric", "numeric",

"numeric", "numeric", "numeric", "numeric",

"numeric", "numeric", "numeric", "numeric",

"numeric", "numeric", "numeric", "numeric",

"numeric", "numeric", "numeric", "numeric",

"numeric", "numeric", "numeric", "numeric",

"numeric", "numeric", "numeric", "numeric"))

names(data)[names(data)=="X2016.child.poverty"] <- "child.pov.2016"

AR_pov <- data %>% subset(State == "KY")

summary(AR_pov)
```




```{r equation, include=FALSE}
equation <- child.pov.2016 ~ rural + urban + lnmanufacturing + lnag +

lnretail + lnhealthss + lnconstruction + lnlesshs +

lnunemployment + lnsinglemom + lnblack + lnhispanic +

lnuninsured + lnincome_ratio + lnteenbirth + lnunmarried
```

## OLS Analysis
How all independent variables relate to child poverty.

```{r ols}
options(scipen = 5)

ols <- lm(equation, data=AR_pov)

summary(ols)
```

```{r visual}
par(mfrow=c(4,4), mar=c(2, 2, 2, 2))
visreg(ols)
```

```{r flips, include=FALSE}
fips <- county.fips

fips.codes <- separate(data = fips, col = polyname, into = c("state", "county"), sep = ",")

md_fips <- subset(fips.codes, state=="kentucky", select=fips)

#library(sf)

se_shp <- st_read(file.path("se_counties/se_counties.shp"))

AR_sf <- se_shp %>% subset(STATE_NAME == "Kentucky")

#library(spdep)
sf_use_s2(FALSE)

neighb.data <- poly2nb(AR_sf, queen=T)

cont.neighb <- nb2listw(neighb.data,style="W", zero.policy = TRUE)

```
## Moran's Correlation
Examining residuals of OLS regression. P value is not significant so that means there is no spatial dependency. 

```{r moran test}
lm.morantest(ols, cont.neighb)
```
## LaGrange Multiplier
Tests different models and compares them to find the best one. None are statistically significant. 
```{r lm test}
lm.LMtests(ols, cont.neighb, test="all")
```


## SLX Model
Do just our neighbors have an impact?
```{r SLX model}
SLX.model <- spatialreg::lmSLX(equation, data=AR_pov, cont.neighb)
summary(SLX.model)

summary(spatialreg::impacts(SLX.model, cont.neighb), zstats = TRUE)[["pzmat"]]

```

## Spatial Lag Model
Our neighbor's value affects both us and our neighbor. 

```{r lag model}

sp.lag.model <- spatialreg::lagsarlm(equation, data=AR_pov, cont.neighb)
summary(sp.lag.model, Nagelkerke = TRUE)
```

```{r lag summary}
summary(spatialreg::impacts(sp.lag.model, listw = cont.neighb, R=100), zstats = TRUE)[["pzmat"]]
```
## Spatial Error Model
Unexplained error function. High residuals mean missing explanatory variable may be spatially correlated. Teen birth and single mom are significant. Lamda is also significant
```{r error model}
sp.err.model <- spatialreg::errorsarlm(equation, data=AR_pov, cont.neighb)
summary(sp.err.model, Nagelkerke = TRUE)
```

## Comparing Models for Contiguity
SLX:
Adjusted R-squared:  0.6343 
p-value: 4.443e-14

Lag:
Nagelkerke pseudo-R-squared: 0.67113
p-value: 0.10203

Err:
Nagelkerke pseudo-R-squared: 0.67867 
p-value: 0.0087167

## Hausman Test
Do the results of the analysis verify use of the model? 

```{r error model test}
spatialreg::Hausman.test(sp.err.model)
```
## Spatial Durbin Model

```{r standard error}
sd.err <- spatialreg::errorsarlm(equation, AR_pov, cont.neighb, etype = "emixed")
sdm <- spatialreg::lagsarlm(equation, AR_pov, cont.neighb, type = "mixed")

```

```{r standard error test}
summary(spatialreg::impacts(sd.err, listw = cont.neighb, R = 100), zstats = TRUE)[["pzmat"]]
```

```{r likelihood ratio}
LR.Sarlm(sd.err,sp.err.model)
```

```{r k neighbors, message=FALSE, warning=FALSE, include=FALSE}
AR.xy <- st_centroid(AR_sf)

#Create neighbors
all.dist.k1 <- knn2nb(knearneigh(AR.xy, k=1, longlat = TRUE))
all.dist.k3 <- knn2nb(knearneigh(AR.xy, k=3, longlat = TRUE))
all.dist.k5 <- knn2nb(knearneigh(AR.xy, k=5, longlat = TRUE))


#Determine max k distance value to neighbor
all.max.k1 <- max(unlist(nbdists(all.dist.k1, AR.xy, longlat=TRUE)))
all.max.k3 <- max(unlist(nbdists(all.dist.k3, AR.xy, longlat=TRUE)))
all.max.k5 <- max(unlist(nbdists(all.dist.k5, AR.xy, longlat=TRUE)))


all.sp.dist.k1 <- dnearneigh(AR.xy, d1=0, d2=1 * all.max.k1, longlat = TRUE)
all.sp.dist.k3 <- dnearneigh(AR.xy, d1=0, d2=1 * all.max.k3, longlat = TRUE)
all.sp.dist.k5 <- dnearneigh(AR.xy, d1=0, d2=1 * all.max.k5, longlat = TRUE)

#Create neighbor list
all.dist.neighb.k1 <- nb2listw(all.sp.dist.k1,style="W", zero.policy = TRUE)
all.dist.neighb.k3 <- nb2listw(all.sp.dist.k3,style="W", zero.policy = TRUE)
all.dist.neighb.k5 <- nb2listw(all.sp.dist.k5,style="W", zero.policy = TRUE)

```
## Distance Lag model

```{r distance lag model}
#Calculate neighbors based on distance
all.dist.lag.k1 <- spatialreg::lagsarlm(equation, data = AR_pov, listw = all.dist.neighb.k1)
all.dist.lag.k3 <- spatialreg::lagsarlm(equation, data = AR_pov, listw = all.dist.neighb.k3)
all.dist.lag.k5 <- spatialreg::lagsarlm(equation, data = AR_pov, listw = all.dist.neighb.k5)
summary(all.dist.lag.k1, Nagelkerke = TRUE)
```


## Distance Error Model

```{r distance error}
all.dist.err.k1 <- spatialreg::errorsarlm(equation, data = AR_pov, listw = all.dist.neighb.k1)
all.dist.err.k3 <- spatialreg::errorsarlm(equation, data = AR_pov, listw = all.dist.neighb.k3)
all.dist.err.k5 <- spatialreg::errorsarlm(equation, data = AR_pov, listw = all.dist.neighb.k5)

summary(all.dist.err.k1, Nagelkerke = TRUE)

```

```{r setting up map, message=FALSE, warning=FALSE, include=FALSE}
dist.err.data <- summary(all.dist.err.k1, correlation=TRUE, Nagelkerke = TRUE)

dist.err.output <- cbind.data.frame(AR_pov$FIPS,
                                    dist.err.data$fitted.values, 
                                    dist.err.data$residual, 
                                    AR_pov$child.pov.2016, 
                                    AR_pov$lnsinglemom, 
                                    AR_pov$lnuninsured, 
                                    AR_pov$lnlesshs, 
                                    AR_pov$lnincome_ratio,
                                    stringsAsFactors = FALSE)

#Renaming columns
colnames(dist.err.output) <- c("fips","fitted","resid","childpov",
                               "single_mom","uninsured","less_hs","income_ratio")
AR_fortify <- fortify(AR_sf)

AR_poly <- merge(x = AR_fortify, y = dist.err.output, 
                 by.x = "FIPS", by.y = "fips", all = TRUE)

```

```{r ready for gg plot, message=FALSE, warning=FALSE, include=FALSE}


bivariate_data <- bi_class(AR_poly, x = childpov, y = single_mom, 
                           dim = 3, style = "quantile")

legend <- bi_legend(pal = "DkViolet",
                    dim = 3,
                    xlab = "Child Poverty",
                    ylab = "Single Mother\n Households",
                    size = 6)

world <- map_data("world")
states <- map_data("state")
southern_states <- subset(states, region %in% 
                            c("texas", "arkansas", "louisiana", "mississippi", 
                              "alabama", "georgia", "florida", "north carolina",
                              "south carolina", "tennessee", "oklahoma", 
                              "kentucky", "west virginia", "virginia", 
                              "maryland", "delaware", "district of columbia"))

```

```{r plot 1, echo=FALSE, message=FALSE, warning=FALSE}
mom_pov_map <- ggplot() + 
  geom_polygon(data = world, aes(x=long,y=lat, group=group), fill = "gray95", color = "white") +
  geom_polygon(data = states, aes(x=long,y=lat, group=group), fill = "gray", color = "white") +
  geom_polygon(data = southern_states, aes(x=long,y=lat, group=group), fill = NA, size = 0.01, color = "white") +  
  geom_sf(data = bivariate_data, aes(fill = bi_class), color = "grey50", show.legend = FALSE) + 
  bi_scale_fill(pal = "DkViolet", dim = 3) +
  coord_sf(crs = 4326, xlim=c(-80,-90), ylim=c(30,40)) +
  theme_void() + theme(legend.title.align=0.5) +
  theme(panel.background = element_rect(fill = 'deepskyblue'),
        panel.grid.major = element_line(colour = NA)) +
  labs(x = "Longitude", y = "Latitude", fill = "Child Poverty", 
       title = "Bivariate Map of Child Poverty and Single Mother Households") +
  theme(plot.title = element_text(face = "bold", hjust = 0.5))
mom_pov_map
```

```{r final map}
final_map <- ggdraw() +
  draw_plot(mom_pov_map, 0, 0, 1, 1) +
  draw_plot(legend, 0.625, 0.025, 0.25, 0.25)
final_map
```

